Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-17 lqg-strings.tex
Added text about relation of scalar density to Kalb-Ramond field.

\subsection{Worldsheet Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}

In the following we will

>>>>

\subsection{(Worldsheet) Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}

In the following we will derive the equations of motion for the bimetric Polyakov action and along the way we will discover that the scalar density $\Delta(x)$ can be identified with the antisymmetric tensor $\epsilon_{ac}$ living on the worldsheet. The worldsheet antisymmetric tensor can itself be understood as arising from the pullback of a bulk antisymmetric tensor. Now, in string theory there is already a very important antisymmetric bulk tensor called the Kalb-Ramond field.
